\cvsection{Work Experience}

\cvexperience
{Senior Software Engineer Consultant}
{The Foxhill Org}
{Sept 2023 – Present}
{Tech Consulting}
{\footnotesize\faCode \hspace{1pt} \cvtag{Figma} \cvtag{Technical Architecture} \cvtag{CI/CD}  \cvtag{Leadership}}
\begin{itemize}
    \item Guided technical aspects to clients on complex software development projects, resulting in significant cost savings and improved efficiency
    \item Conducted technical assessments and made recommendations for improving existing systems and processes.
    \item Implemented DevOps CI/CD practices, including automated testing and continuous integration/deployment.

\end{itemize}

\medskip

\cvexperience
{Founder}
{Shared Creatives}
{Nov 2023 – Present}
{Tech Consulting}
{\footnotesize\faCode \hspace{1pt} \cvtag{Collaboration} \cvtag{Business Development} \cvtag{Leadership}}
\begin{itemize}
    \item Developed and maintained web applications for clients across various industries.
    \item Built partnerships and collaborations with technology vendors, marketing agencies, and design firms to offer comprehensive digital solutions that enriched the e-commerce ecosystem for clients.
    \item Drove business strategy and growth, expanding the client base and portfolio by consistently exceeding expectations in functionality, design, and user engagement.
\end{itemize}

\medskip

\cvexperience
{Senior Software Engineer Consultant}
{UnitedHealth Group}
{March 2021 – Nov 2023}
{Healthcare}
{\footnotesize\faCode \hspace{.5pt} \cvtag{React Native} \cvtag{TypeScript} \cvtag{GraphQL} \cvtag{Jest} \cvtag{TDD} \cvtag{Redux} \cvtag{Storybook} \cvtag{Leadership}}
\begin{itemize}
    \item Upgraded legacy components inside the UHG React Native application with TypeScript improving functionality, maintainability, and code quality.
    \item Executed unit tests using Jest, ensuring high code quality and reliability through Test-Driven Development (TDD).
    \item Provided mentorship and guidance to junior developers, focusing on best practices and strategies to improve employee engagement and team productivity, leading to a 10\% improvement in team efficiency.
\end{itemize}

\medskip

\cvexperience
{Senior Software Engineer Consultant}
{Optum Group}
{March 2021 – Sept 2022}
{Healthcare}
{\footnotesize\faCode \hspace{1pt} \cvtag{Storybook} \cvtag{Atomic Design} \cvtag{TypeScript} \cvtag{React-Native} \cvtag{Redux} \cvtag{TDD}}
\begin{itemize}
    \item Provided guidance to junior developers, resulting in a 15\% improvement in employee engagement and overall team performance.
    \item Piloted the use of component-driven development and atomic design principles on both client and internal projects, demonstrating increased developer efficiency and ease of collaboration with design teams.
    \item Collaborated closely with stakeholders at UnitedHealthcare (UHC) to conceptualize, design, and develop a user-friendly application tailored for broker users, meeting specific user needs and enhancing usability.
\end{itemize}

\medskip

\cvexperience
{Full Stack Software Engineer}
{Prep Network}
{March 2020 – Aug 2020}
{Ecommerce}
{\footnotesize\faCode \hspace{1pt} \cvtag{Laravel} \cvtag{Redis} \cvtag{MySQL} \cvtag{PHP} \cvtag{React Native} \cvtag{LAMP} \cvtag{APIs}}
\begin{itemize}
    \item Engineered server-side logic using Laravel, resulting in a 25\% improvement in application performance and achieving seamless integrations with 5+ third-party platforms.
    \item Updated features within their React Native ticketing app by formulating reusable, effective, and scalable JavaScript code.
    \item Developed and maintained the Prep Network website, ensuring optimal performance and user experience through continuous monitoring and troubleshooting.
\end{itemize}
\medskip
\cvexperience
{Full Stack Engineer III}
{The Star Tribune}
{April 2018 – March 2020}
{Media}
{\footnotesize\faCode \hspace{1pt} \cvtag{React-Native} \cvtag{Microservices} \cvtag{GraphQL} \cvtag{Node.js} \cvtag{C++} \cvtag{Java} \cvtag{Jest}}
\begin{itemize}
    \item Led development efforts for the Star Tribune app, leveraging the React Native library to allow easier adaptation and improved user experiences.
    \item Managed updating, maintaining, and fixing Version 2.0 of the app, carrying out major upgrades with React Native while supporting the existing codebase.
    \item Maintained custom libraries in Java and C++ to optimize system performance and extend functionality for enterprise-level software solutions, leading to a 30\% improvement in processing efficiency.
\end{itemize}

\medskip

\cvexperience
{Software Engineer}
{Irish Titan}
{Feb 2018 – Feb 2019}
{Ecommerce}
{\footnotesize\faCode \hspace{.5pt} \cvtag{Shopify} \cvtag{Magento} \cvtag{Wordpress} \cvtag{Drupal} \cvtag{JavaScript} \cvtag{HTML} \cvtag{CSS}}
\begin{itemize}
    \item Applied advanced Shopify Liquid templating language to create dynamic and responsive storefronts, optimizing user experience and conversion rates.
    \item Utilized HTML, CSS, and JavaScript to customize Shopify themes, ensuring pixel-perfect designs and seamless integration of additional functionalities.
\end{itemize}

\medskip
\cvexperience
{Contract Web Developer}
{JAMF}
{April 2017 – Oct 2017}
{Technology}
{\footnotesize\faCode \hspace{1pt} \cvtag{AngularJS} \cvtag{TypeScript}}
\begin{itemize}
    \item Collaborated on enhancing the user experience of version 9.9 of the JSS, implementing AngularJS with TypeScript to introduce new features and optimize performance, while strategically preparing for a comprehensive UI overhaul in V10.
    \item Worked with the JAMF pattern library to streamline development processes and maintain consistency in UI design and implementation, enhancing productivity and facilitating code reuse.
\end{itemize}

\medskip

\cvexperience
{Software Engineer}
{Gander Mountain}
{Sept 2016 – January 2017}
{Ecommerce}
{\footnotesize\faCode \hspace{1pt} \cvtag{JavaScript} \cvtag{CSS} \cvtag{HTML} \cvtag{Bootstrap} \cvtag{SASS} \cvtag{Agile}}
\begin{itemize}
    \item Led the refinement of our ecommerce frontend architecture, implementing modern development practices and emphasizing the strategic use of media queries for optimal responsiveness.
    \item Leveraged expertise in responsive design and frontend technologies to drive the evolution of Gander Mountain's platform, ensuring seamless adaptation to various devices and screen sizes.
    \item Collaborated closely with UX developers, utilizing JavaScript, CSS, and HTML to redesign product page displays, optimizing visual appeal and usability for customers.
\end{itemize}


\medskip
\cvexperience
{Contract Frontend Software Engineer}
{AIMIA}
{May 2015 – June 2016}
{Marketing}
{\footnotesize\faCode \hspace{1pt} \cvtag{UX/UI} \cvtag{Analytics} \cvtag{HTML} \cvtag{SASS} \cvtag{jQuery} \cvtag{CSS3}}
\begin{itemize}
    \item Worked with high-profile clients including Hallmark, Nature’s Bounty, GreyHound, Pampers, and Kellogg.
    \item Devised frontend development strategies and solutions for our partner SmartButton SaaS product.
    \item Managed user web analytics tracking for performance optimization.
\end{itemize}

\medskip
\cvexperience
{Associate Web Developer}
{Capella University}
{April 2014 – April 2015}
{Development}
{\footnotesize\faCode \hspace{1pt} \cvtag{WAG} \cvtag{.NET} \cvtag{Liferay} \cvtag{HTML5} \cvtag{SASS} \cvtag{RESTapi} \cvtag{Accessability}}
\begin{itemize}
    \item Architected and tailored Liferay portals using Java and .NET interoperability; boosted user engagement by 30\% and improved business processes, leading to a 20\% reduction in operational inefficiencies.
    \item Acted as a lead researcher and ambassador for Web Accessibility Guidelines (WAG) 2.0, ensuring all frontend developments adhered to accessibility standards, enhancing usability for all users.
\end{itemize}

\medskip

\cvexperience
{Contract Software Developer}
{Horizon Integrations @ 3M}
{July 2014 – Nov 2014}
{eCommerce}
{\footnotesize\faCode \hspace{1pt} \cvtag{PHP} \cvtag{Magento} \cvtag{CSS} \cvtag{JavaScript}}
\begin{itemize}
    \item Proficient in Magento 1.x and 2.x development, including custom module development, theme customization, and performance optimization
    \item Strong understanding of Magento's architecture, database schema, and caching mechanisms.
\end{itemize}

